Using tours to visually investigate properties of new projection pursuit indexes with application to problems in physics

### 2018-11-02 scagnostics.Rmd
got table formatted nicely

```{r load}
library(tourr)
library(tidyverse)
library(reshape2)
library(scagnostics)
library(gridExtra)
library(tictoc) #timer
library(mbgraphic) #Katrins package
library(GGally)
library(geozoo)
library(minerva) #MINE indices
```

@@

```{r indexTable, echo=FALSE}
tableTemp <- function(){
  tibble(
    index=character(),
    data=character(),
    size=numeric(),
    structured=character(),
    value5=numeric(),
    value95=numeric()
  )
}

@@

getIdx <- function(dataT, size, structured){
  convex <- numeric(length = 100)
  skinny <- numeric(length = 100)
  stringy <- numeric(length = 100)
  micidx <- numeric(length = 100)
  ticidx <- numeric(length = 100)
  dcor2D <- numeric(length = 100)
  splines2D <- numeric(length = 100)
  for(i in 1:100){
    cSample <- getSample(dataT, size)
    if(!structured){
      x = as.numeric(cSample$V1)
      y = as.numeric(cSample$V2)
    } else{
      x = as.numeric(cSample$V5)
      y = as.numeric(cSample$V6)
    }
    scag <- scagnostics(x=x, y=y)$s
    midx <- mine(x, y, est = "mic_e")
    skinny[i] <- scag["Skinny"]
    stringy[i] <- scag["Stringy"]
    convex[i] <- scag["Convex"]
    micidx[i] <- midx$MIC
    ticidx[i] <- midx$TIC
    dcor2D[i] <- dcor2d(x=x, y=y)
    splines2D[i] <- splines2d(x,y)
  }
  lapply(c(skinny, stringy, convex, micidx, ticidx, dcor2D, splines2D), sort)
  res <- tableTemp() %>%
    add_row(index="Skinny", data=dataT, size=size,
            structured=ifelse(structured, "yes", "no"),
            value5=skinny[5], value95=skinny[95]) %>%
    add_row(index="Stringy", data=dataT, size=size,
            structured=ifelse(structured, "yes", "no"),
            value5=stringy[5], value95=stringy[95]) %>%
    add_row(index="Convex", data=dataT, size=size,
            structured=ifelse(structured, "yes", "no"),
            value5=convex[5], value95=convex[95]) %>%
    add_row(index="MICe", data=dataT, size=size,
            structured=ifelse(structured, "yes", "no"),
            value5=micidx[5], value95=micidx[95]) %>%
    add_row(index="TICe", data=dataT, size=size,
            structured=ifelse(structured, "yes", "no"),
            value5=ticidx[5], value95=ticidx[95]) %>%
    add_row(index="dcor2D", data=dataT, size=size,
            structured=ifelse(structured, "yes", "no"),
            value5=dcor2D[5], value95=dcor2D[95]) %>%
    add_row(index="splines2D", data=dataT, size=size,
            structured=ifelse(structured, "yes", "no"),
            value5=splines2D[5], value95=splines2D[95])
}

if(!file.exists("cache/indexTable.rda")){
  set.seed(505)
  res <- tableTemp()
  for(ds in c("Pipe", "Sine", "Spiral")){
    for (size in c(100, 1000)){
      for (structured in c(TRUE, FALSE)){
        res <- full_join(res,getIdx(ds, size, structured))
      }
    }
  }
  save(res, file = "cache/indexTable.rda")
} else {
  load("cache/indexTable.rda")
}
knitr::kable(res,  caption = "Summary of index values.", digits=2) 
```

>>>>

```{r load}
library(tourr)
library(tidyverse)
library(reshape2)
library(scagnostics)
library(gridExtra)
library(tictoc) #timer
library(mbgraphic) #Katrins package
library(GGally)
library(geozoo)
library(minerva) #MINE indices
library(kableExtra)
library(forcats)
```

@@

```{r indexTable, echo=FALSE}
tableTemp <- function(){
  tibble(
    index=character(),
    data=character(),
    size=numeric(),
    type=character(),
    value5=numeric(),
    value95=numeric()
  )
}

@@

getIdx <- function(dataT, size, type){
  convex <- numeric(length = 100)
  skinny <- numeric(length = 100)
  stringy <- numeric(length = 100)
  micidx <- numeric(length = 100)
  ticidx <- numeric(length = 100)
  dcor2D <- numeric(length = 100)
  splines2D <- numeric(length = 100)
  for(i in 1:100){
    cSample <- getSample(dataT, size)
    if(type == "noise"){
      x = as.numeric(cSample$V1)
      y = as.numeric(cSample$V2)
    } else{
      x = as.numeric(cSample$V5)
      y = as.numeric(cSample$V6)
    }
    scag <- scagnostics(x=x, y=y)$s
    midx <- mine(x, y, est = "mic_e")
    skinny[i] <- scag["Skinny"]
    stringy[i] <- scag["Stringy"]
    convex[i] <- scag["Convex"]
    micidx[i] <- midx$MIC
    ticidx[i] <- midx$TIC
    dcor2D[i] <- dcor2d(x=x, y=y)
    splines2D[i] <- splines2d(x,y)
  }
  lapply(c(skinny, stringy, convex, micidx, ticidx, dcor2D, splines2D), sort)
  res <- tableTemp() %>%
    add_row(index="skinny", data=dataT, size=size,
            type=type,
            value5=skinny[5], value95=skinny[95]) %>%
    add_row(index="stringy", data=dataT, size=size,
            type=type,
            value5=stringy[5], value95=stringy[95]) %>%
    add_row(index="convex", data=dataT, size=size,
            type=type,
            value5=convex[5], value95=convex[95]) %>%
    add_row(index="MICe", data=dataT, size=size,
            type=type,
            value5=micidx[5], value95=micidx[95]) %>%
    add_row(index="TICe", data=dataT, size=size,
            type=type,
            value5=ticidx[5], value95=ticidx[95]) %>%
    add_row(index="dcor2D", data=dataT, size=size,
            type=type,
            value5=dcor2D[5], value95=dcor2D[95]) %>%
    add_row(index="splines2D", data=dataT, size=size,
            type=type,
            value5=splines2D[5], value95=splines2D[95])
}

if(!file.exists("cache/indexTable.rda")){
  set.seed(505)
  res <- tableTemp()
  for(ds in c("Pipe", "Sine", "Spiral")){
    for (size in c(100, 1000)){
      for (type in c("structure", "noise")){
        res <- bind_rows(res,getIdx(ds, size, type))
      }
    }
  }
  res <- res %>% arrange(data, size, index, type) %>% select(data, size, index, type, value5, value95)
  save(res, file = "cache/indexTable.rda")
} else {
  load("cache/indexTable.rda")
}
resp <- res %>% filter(size == 1000, data == "Pipe") %>%
  select(index, type, value95, value5) %>%
  rename(lower=value95, upper=value5)
resi <- res %>% filter(size == 1000, data == "Sine") %>%
  select(index, type, value95, value5) %>%
  rename(lower=value95, upper=value5)
ress <- res %>% filter(size == 1000, data == "Spiral") %>%
  select(index, type, value95, value5) %>%
  rename(lower=value95, upper=value5)
res_all <- bind_cols(resp, resi, ress) %>%
  select(-index1, -type1, -index2, -type2) %>%
  mutate(index = fct_relevel(index, "convex", "skinny", "stringy", "dcor2D", "splines2D", "MICe", "TICe")) %>%
  mutate(index = c("convex", "", "skinny", "", "stringy", "", "dcor2D", "", "splines2D", "", "MICe", "", "TICe", ""))
# Good resource for doing tables
# https://cran.r-project.org/web/packages/kableExtra/vignettes/awesome_table_in_pdf.pdf
kable(res_all, format = "latex",  caption = "Comparison of index values between noise projections and structured projections for sample size 1000, using 5th and 95th percentiles from 100 simulated sets. Most indices have much larger values for the structured projections, except for convex.", 
      col.names=c("Index","", "lower", "upper", "lower", "upper", "lower", "upper"),
      digits=2, booktabs = T) %>% 
      add_header_above(c(" ", " ", "pipe" = 2, "sine" = 2, "spiral"=2)) %>%
  group_rows("", 1, 2) %>%
  group_rows("", 3, 4) %>%
  group_rows("", 5, 6) %>%
  group_rows("", 7, 8) %>%
  group_rows("", 9, 10) %>%
  group_rows("", 11, 12) %>%
  group_rows("", 13, 14) %>%
  kable_styling(position = "center")
```
